\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-12 smurf_paper.tex
After much discussion Wayne Holland is now an author

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2}$\thanks{E-mail:~echapin@sciops.esa.int,
      Present address: XMM SOC, ESAC, Apartado 78, 28691 Villanueva de
      la Ca\~nada, Madrid, Spain},
    David~S.~Berry$^{2}$,
    Andrew~G.~Gibb$^{1}$,
    Tim~Jenness$^{2}$,
    Douglas~Scott$^{1}$,
    Remo~P.~J.~Tilanus$^{2,3}$,
    Frossie~Economou$^2$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA},
  }
  \\
  \\
  $^{1}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{2}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA\\
  $^{3}$Netherlands Organisation for Scientific Research,
  Laan van Nieuw Oost-Indie 300, NL-2509 AC The Hague, The Netherlands}
\begin{document}

@@

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation.  This research was supported in part by the
Natural Sciences and Engineering Research Council of Canada.  EC
thanks CANARIE/CANFAR for additional funding.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou, Jessica
Dempsey, and Wayne Holland.  We also thank Mark Halpern, Matthew
Hasselfield, and Gaelen Marsden for many useful discussions, and
observers who provided helpful feedback; especially David Nutter and
Todd McKenzie.  We acknowledge the contributions of Dennis Kelly, Alex
van Engelen and Jennifer Balfour for early investigations related to
SMURF; and Mark Thompson, Craig Walther and S\'{e}verin Gaudet for
being on the Critical Design Review panel. Finally, we thank Per
Friberg and Gary Davis for their helpful comments on the manuscript.

>>>>

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2}$\thanks{E-mail:~echapin@sciops.esa.int,
      Present address: XMM SOC, ESAC, Apartado 78, 28691 Villanueva de
      la Ca\~nada, Madrid, Spain},
    David~S.~Berry$^{2}$,
    Andrew~G.~Gibb$^{1}$,
    Tim~Jenness$^{2}$,
    Douglas~Scott$^{1}$,
    Remo~P.~J.~Tilanus$^{2,3}$,
    Frossie~Economou$^2$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719,
      USA},
    Wayne ~S.~Holland$^{4,5}$
  }
  \\
  \\
  $^{1}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{2}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA\\
  $^{3}$Netherlands Organisation for Scientific Research,
  Laan van Nieuw Oost-Indie 300, NL-2509 AC The Hague, The Netherlands\\
  $^{4}$UK Astronomy Technology Centre, Royal Observatory, Blackford
  Hill, Edinburgh EH9 3HJ\\
  $^{5}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill Edinburgh, EH9 3HJ}
\begin{document}

@@

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation.  This research was supported in part by the
Natural Sciences and Engineering Research Council of Canada.  EC
thanks CANARIE/CANFAR for additional funding.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou and Jessica
Dempsey.  We also thank Mark Halpern, Matthew
Hasselfield, and Gaelen Marsden for many useful discussions, and
observers who provided helpful feedback; especially David Nutter and
Todd McKenzie.  We acknowledge the contributions of Dennis Kelly, Alex
van Engelen and Jennifer Balfour for early investigations related to
SMURF; and Mark Thompson, Craig Walther and S\'{e}verin Gaudet for
being on the Critical Design Review panel. Finally, we thank Per
Friberg and Gary Davis for their helpful comments on the manuscript.
